---
title: "Static Website for FM Housing Data"
author: "Ella"
date: "2024-09-20"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)


# load data
house_data <- read.csv("https://raw.githubusercontent.com/gmtanner-cord/DATA470-2024/refs/heads/main/fmhousing/FM_Housing_2018_2022_clean.csv")

knitr::opts_chunk$set(echo = TRUE)
```
```{r}
# copy model from model.R

model = lm(Sold.Price ~ Total.Bedrooms + Total.Bathrooms, data = house_data)




```

## Total Bedrooms in FM Houses

The majority of houses in the FM area have 3-4 bedrooms.

```{r}
Bedrooms <- house_data$Total.Bedrooms
hist(Bedrooms)
```

## Total Bathrooms in FM Houses

The majority of houses in the FM area have 2-3 bathrooms.

```{r}
Bathrooms <- house_data$Total.Bathrooms
hist(Bathrooms)
```

There is a positive relationship between total bathrooms in a house and sold price

```{r}
ggplot(house_data) +
  # total bathrooms vs sold price
  geom_point(aes(x = Total.Bathrooms, y = Sold.Price), color = "blue", alpha = 0.6) +
  geom_smooth(aes(x = Total.Bathrooms, y = Sold.Price), color = "red", method = "lm", se = FALSE) +
  labs(
    title = "Total Bathrooms vs Sold Price",
    x = "Total Bathrooms",
    y = "Sold Price"
  ) 
```

There is a positive relationship between total bedrooms in a house and sold price

```{r}
ggplot(house_data) +
  # total bedrooms vs sold price
  geom_point(aes(x = Total.Bedrooms, y = Sold.Price), color = "blue", alpha = 0.6) +
  geom_smooth(aes(x = Total.Bedrooms, y = Sold.Price), color = "red", method = "lm", se = FALSE) +
  labs(
    title = "Total and Bedrooms vs Sold Price",
    x = "Total Bedrooms",
    y = "Sold Price"
  ) 
```


Model's Predicted Values vs actual Sold Price

```{r}
house_data$Predicted.Price <- predict(model, newdata = house_data)

ggplot(house_data, aes(x = Sold.Price, y = Predicted.Price)) +
  geom_point(aes(color = "Predicted Values"), alpha = 0.5) + 
  geom_abline(aes(color = "Perfect Fit"), slope = 1, intercept = 0, linetype = "dashed", size = 1) + 
  labs(title = "Predicted vs. Actual Sold Price",
       x = "Actual Sold Price", y = "Predicted Sold Price") +
  scale_color_manual(name = "Legend", values = c("Predicted Values" = "blue", "Perfect Fit" = "red")) + 
  theme_minimal()


```
